\begin{abstract}

% Interdomain path changes occur frequently. Because routing protocols
% expose insufficient information to reason about all changes,
% the general problem of identifying the root cause remains
% unsolved. This has implications for large service providers,
% cloud operators, ISPs, networking researchers and protocol
% design. 

Interdomain path changes occur frequently. Because routing protocols
expose insufficient information to reason about all changes, the general
problem of identifying the root cause remains unsolved.  In this work,
we design and evaluate \ouralgo, a real-time system that allows a
provider to accurately isolate the root cause (the network responsible)
of path changes affecting its prefixes.  First, we develop a new model
describing path changes and use it to provably identify the set of all
potentially responsible networks. Next, we develop a recursive algorithm
that accurately isolates the root cause of any path change. We observe
that the algorithm requires monitoring paths that
are generally not visible using standard measurement tools. To address
this limitation, we combine existing measurement tools in new ways to
acquire path information required for isolating the root cause of a path
change.  We evaluate \ouralgo on path changes obtained through
controlled Internet experiments, simulations, and `in the wild'
measurements. We demonstrate that \ouralgo is highly accurate, works
well even with partial information, and generally narrows down the root
cause to a single network or two neighboring ones.  On controlled
experiments \ouralgo is 100\% accurate, as opposed to prior work which
is accurate only 61.7\% of the time.  


% In this work, we design and evaluate \ouralgo, a real-time system that
% allows a provider to accurately isolate the root cause (the network
% responsible) of path changes affecting their prefixes.  First, we
% develop a new model describing path changes and use it to provably
% identify the set of all potentially responsible networks. We then use
% empirically validated assumptions about routing policy to further
% restrict this set. Next, we develop a recursive algorithm that
% accurately isolates the root cause of any path change. We observe that
% the algorithm requires monitoring available-but-inactive paths that
% are generally not visible using standard measurement tools. To address
% this limitation, we combine existing measurement tools in new ways to
% acquire path information required for isolating the root cause of a
% path change.  We evaluate \ouralgo on path changes obtained through
% controlled Internet experiments, simulations and `in-the-wild'
% measurements. We demonstrate that \ouralgo is highly accurate, works
% well even with partial information, and generally narrows down the
% root cause to a single network or two neighboring ones.  On controlled
% experiments \ouralgo is 100\% accurate, as opposed to prior work which
% is accurate only 61.7\% of the time.  

\end{abstract}


% A category with the (minimum) three required fields
\category{C.2.2}{Communication Networks}{Network Operations: Network Monitoring }
\keywords{Path Changes, Root Cause Analysis, Measurement,
Monitoring, BGP}
