\begin{comment}
To show the incremental benefit of
each measurement layer in our system we do our analysis starting with just the
RouteViews feed (RV), followed by RouteViews combined with forward traceroutes
from PlanetLab nodes (RV+PL), and finally followed by these two feeds combined
with Reverse Traceroute (RV+PL+REVTR). 

Table \ref{tab:ss-beg} refers to a series of 4500 path changes. It shows the
percentage of paths for each layer where the candidate set computed at the
beginning contained the ground truth, i.e., the AS poisoned or unpoisoned.
Depending on the coverage provided by each measurement feed, some ASes from the
ideal candidate set, i.e., $N(O(S)) \cup O(N(S))$ might be missing from the
computed candidate set, including the poiosned/unpoisoned AS.

This is primarily due to the lack of measurements available from certain ASes.
Although route data taken directly from BGP tables is generally more reliable
that data plane measurements, the lack of a widely deployed RouteViews-like
measurement infrastructure means that the scope of monitoring paths to a
limited set of nodes is quite limited. 

\subsubsection{Root Cause Analysis with Control-Plane Measurements}

We had a total of $33$ RouteViews peers collecting paths toward the muxes. For
a series of poisonings we observed $741$ path changes, from control plane as
well as data plane, including $133$ induced path changes. In $401$ cases
\emph{Javed} was able to identify the correct AS poisoned or unpoisoned in its
suspect set. This is an accuracy of $54\%$. The algorithm was not able to
identify any of the induced path changes. The reason for such low accuracy is
lack of relevant measurements. In the relatively simple cases of non-induced
path changes where \emph{Javed} was not able to identify the correct
root-cause, there were no measurement from the poisoned/unpoisoned AS
before/after the poisoning $95\%$ of the time. Overall $20\%$ of the ASes had
no measurements available before/after the poisoning.

\subsubsection{Root Cause Analysis with Data-Plane Measurements}

After establishing the insufficiency of BGP feeds, we add traceroute
measurements from our set of distributed PlanetLab vantage points. This
drastically improves the accuracy of \emph{Javed} as the relevant measurements
are now available when needed.  {\color{blue}{say something about sources of
inaccuracies and how you deal with it: a) routers occasionally not responding.
b) the inaccuracy of ip2as translation.}} Given a choice between a RouteViews
path and a traceroute from AS $X$, the RV path is preferred over the traceroute
since control-plane reflects the routing state more accurately then data-plane.

We had a total of  approximately $200$ globally distributed PlanteLab vantage
points collecting trace route paths toward the muxes in addition to the. For the
same set of path changes as before, \emph{Javed}'s accuracy goes up to $84\%$.
The induced path change detection accuracy is $20\%$. 

(1) How often is it exact, close, or wrong? \

(2) For those that are not exact, classify the reasons why it is wrong. \

(3) What is the number of ASes that we need to monitor to capture enough
information for pinpointing the AS responsible for path changes? How does this
change as you increase the number of ASNs from which we can do root cause
analysis?\

(4) What fraction of the time is each dataset used to identify the root cause?
Is it mostly RV, traceroutes, revtr? In other words, what is the marginal
utility of each dataset? How useful was the study using exhaustive prepending
and poisoning?
\end{comment}
